The Weakly Nonlinear Magnetorotational Instability

### 2016-09-02 paper/widegap_mri_paper.tex
summary

@@

>>>>

In this work we carry out a formal weakly nonlinear multiple scales analysis of the MRI in a Taylor Couette flow. We examine both the standard MRI, in which the background magnetic field is purely axial, as well as the helical MRI, in which the background magnetic field also contains an azimuthal component. We find that in both cases the amplitude of the weakly nonlinear system is governed by a Ginzburg-Landau equation, but the GLE is real in the case of the standard MRI and complex for the helical MRI. We examine the $Pm$ dependence of the saturation amplitude of the standard MRI, making explicit comparison to the $Pm$ scaling behavior of this system in the narrow gap limit.

@@

The theory presented here may be extended in several ways.
